### 2017-08-25 paper/evaluation.tex
pass o subjects section

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
  or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from README file (not
other code elements); it does not provide a feature to search for
projects containing certain files in the dir structure (\eg{},
\emph{pom.xml}).  Figure~\ref{fig:subject-query} illustrates the query
to the \github{} API as an HTTP request.

\vspace{1ex}
\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
        +stars:>=100+pushed:>=2016-01-01
        +mvn%20in:readme+sort:stars
\end{lstlisting}
    \caption{\label{fig:subject-query} Query to the \github{} API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

After obtaining a list of potential projects, we filtered those
containing a \pomf{} file in the root directory.  A Maven project may
contain several sub-modules with multiple \pomf{} files.\Comment{  We
based our methodology to select experimental subjects on other recent
studies in testing and
debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.} As of
March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
    hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotCompilable{} uncompilable projects, and
    \SubjectsGithubNotTestable{} untestable projects\Comment{, and
    \SubjectsGithubFlaky{} projects with flaky tests}. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}

From \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotCompilable{} were unable to compile due
to missing dependencies, and \SubjectsGithubNotTestable{} projects
were untestable due to incompatible testing environment.  We also
found \SubjectsGithubFlaky{} projects with ``flaky'' tests.  We
considered those projects but ignored their tests (using JUnit's
\CodeIn{@Ignore} annotation) as to avoid measurement noise.  To detect
those projects, we executed every test suite for three times.  Our
final set of subjects consists of \numSubjs{} projects.

>>>>

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
in the dir structure (\eg{}, \emph{pom.xml}).
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.

\vspace{1ex}
\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
        +stars:>=100+pushed:>=2016+mvn%20in:readme
        &sort=stars
\end{lstlisting}
    \caption{\label{fig:subject-query} Query to the \github{} API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

After obtaining a list of potential projects, we filtered those
containing a \pomf{} file in the root directory.  A Maven project may
contain several sub-modules with multiple \pomf{} files.\Comment{  We
based our methodology to select experimental subjects on other recent
studies in testing and
debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.}
Also, to avoid bias in our experiments, we executed multiple times all
test suites from our sample set to detect and discard subjects with
\emph{flaky tests}. \Fix{Discuss briefly test flakiness}.
As of August 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. 
From \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \Comment{ were unable to compile due
to missing dependencies,} and \SubjectsGithubNotTestable{} projects
were untestable due to incompatible testing environment.  We also
found \SubjectsGithubFlaky{} projects with ``flaky'' tests.  We
considered those projects but ignored their tests (using JUnit's
\CodeIn{@Ignore} annotation) as to avoid measurement noise.  To detect
those projects, we executed every test suite for three times.  Our
final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
    hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotTestable{} untestable projects, and
    \SubjectsGithubFlaky{} projects with flaky tests. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}
